Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
1st paragraph

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization. An increasing number of visits generally correlates with higher chances of fertilization (Refs). However this is not always the case, among these flower visitors we find also nectar robbers and pollen thiefs (Refs) or pollen quality (example with ref?). Moreover, other less studies issues in the pollination process such as conspecific pollen loss or the arrival of foreign pollen can have detrimental effects for the species fitness @morales2008.

>>>>

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization. An increasing number of visits generally correlates with higher chances of fertilization (Refs). However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs). Moreover, other less studies issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008.

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
1st paragraph

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and therefore
ovule fertilization. An increasing number of visits generally correlates
with higher chances of fertilization (Refs). However this is not always
the case, among these flower visitors we find also nectar robbers and
pollen thiefs (Refs) or pollen quality (example with ref?). Moreover,
other less studies issues in the pollination process such as conspecific
pollen loss or the arrival of foreign pollen can have detrimental
effects for the species fitness Morales and Traveset (2008).

>>>>

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and therefore
ovule fertilization. An increasing number of visits generally correlates
with higher chances of fertilization (Refs). However this is not always
the case, among these possible flower visitors we find also nectar
robbers and pollen thiefs (Refs) and the quality of pollen that is
deposited on the stigma is also highly relevant to the pollination
succes (Refs). Moreover, other less studies issues in the pollination
process are conspecific pollen loss and the arrival of foreign pollen
which can have important detrimental effects for the species fitness
Morales and Traveset (2008).
